An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-17 indicators/paper/paper.tex
Add first group of authors

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,c,1]{Author One}
\author[b,1,2]{Author Two}
\author[a]{Author Three}

\affil[a]{Affiliation One}
\affil[b]{Affiliation Two}
\affil[c]{Affiliation Three}

% Please give the surname of the lead author for the running footer
\leadauthor{Lead author last name}

@@

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any competing interests here.}
\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}

>>>>

% Use letters for affiliations, numbers to show equal authorship (if applicable)
% and to indicate the corresponding author

% Writing group
\author[a,1]{Alex Reinhart}
\author[b,2]{Logan Brooks}
\author[a,2]{Maria Jahja}
\author[b,2]{Aaron Rumack}
\author[c,2]{Jingjing Tang}

% Middle authors
\author[d]{Middle Authors to be Added}

% Senior authors
\author[b]{Roni Rosenfeld}
\author[a]{Ryan Tibshirani}

\affil[a]{Department of Statistics \& Data Science, Carnegie Mellon University}
\affil[b]{Machine Learning Department, Carnegie Mellon University}
\affil[c]{Department of Computational Biology, Carnegie Mellon University}
\affil[d]{Remaining affiliations to be added}

% Please give the surname of the lead author for the running footer
\leadauthor{Reinhart}

@@

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any competing interests here.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: areinhar@stat.cmu.edu}
\equalauthors{\textsuperscript{2}L.B., M.J., A.R., and J.T. contributed equally
  to this work.}
